Performing and evaluating graph-based clustering with rOpenScPCA

### 2024-10-09 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
Add initial code files, without much code yet but to set the stage for later

---
title: "cell-type-nonETP-ALL-03 Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

This a template for an analysis notebook using R Markdown.

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title:` and `author:` fields in the YAML header at the top of the document.

Don't forget to rename this file as well!

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

```{r packages}
# load required packages
# e.g. library(tidyverse)
```

You may also want to use the `package::function()` syntax within your code for better tracking of which functions come from which packages, and to avoid conflicts between functions with the same name in different packages.

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-nonETP-ALL-03")
```

>>>>

---
title: "Performing and evaluating graph-based clustering with rOpenScPCA"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

@@

@@

```{r packages}
# load required packages
library(rOpenScPCA)
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(Seurat)
  library(dplyr)
  library(ggplot2)
})
```

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "hell-c")
```
